On particular diameter bounds for integral point sets in higher dimensions \footnote{ This work was carried out at Voronezh State University and supported by Russian Science Foundation grant 19-11-00197. }

### 2025-02-24 AvdMomZvol_rails/Article.tex
[rails] Adjust the authors metadata

%% Прекрасно понимаю, что следующая команда - дичь и вордописчество, но время не ждёт, время жмёт
\author{
	Avdeev N.N.
	\footnote{nickkolok@mail.ru, avdeev@math.vsu.ru}
	, Zvolinsky R.E., Momot E.A.
	\\
	\\
	\emph{Voronezh State University}
}

@@

>>>>

%% Прекрасно понимаю, что следующая команда - дичь и вордописчество, но время не ждёт, время жмёт
\author{
	Avdeev N.N.
	\footnote{nickkolok@mail.ru, avdeev@math.vsu.ru}
	, Zvolinskii R.E., Momot E.A.
	\\
	\\
	\emph{Voronezh State University}
}

@@

Авдеев Николай Николаевич

Воронежский государственный университет, кафедра теории функций и геометрии, аспирант

Россия, 394018, г. Воронеж, Университетская пл., 1

E-mail: nickkolok@mail.ru, avdeev@math.vsu.ru

Avdeev Nikolai Nikolaevich

Voronezh State University, Department of Function Theory and Geometry, postgraduate student

Russia, 394018, Voronezh, University sq., 1

Зволинский Роман Евгеньевич

Воронежский государственный университет, кафедра теории функций и геометрии, аспирант

Россия, 394018, г. Воронеж, Университетская пл., 1

E-mail: roman.zvolinskiy@gmail.com , roman-zvolinskiy@mail.ru

Zvolinskii Roman Evgen'evich

Voronezh State University, Department of Function Theory and Geometry, postgraduate student

Russia, 394018, Voronezh, University sq., 1

Момот Екатерина Александровна

Воронежский государственный университет, кафедра функционального анализа и операторных уравнений, выпускница

Россия, 394018, г. Воронеж, Университетская пл., 1

Momot Ekaterina Alexandrovna

Voronezh State University, Department of Functional Analysis and Operator Equations (graduated from)

Russia, 394018, Voronezh, University sq., 1
